PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2023-03-07 refereeResponse.txt

490: How could such an enhancement in planetesimal surface density be achieved initially? Is this initial condition consistent with planetesimal formation models, e.g. Dra̧żkowska & Dullemond 2018, Lenz et al 2019.
493: What is the motivation behind variation in the power-law index? Is there significant uncertainty in the MMSN power law index?
499: Maybe elaborate on why this equilibrium is physical? Are there other works which use the same balance to inform initial conditions?
504: missing respectively. And semi-major axes.
505: When is the Stokes regime valid, and what does it mean?
506: The letter tau is used for a timescale just above, but now it says t. I would recommend staying consistent. Tau tends to be used for dimensionless timescales, so I would probably go with t_s and t_vs.
511: Solid-to-gas surface density ratio of 1/240 seems very small, especially given that the authors are considering the solid surface density to already be enhanced by a factor of 100. Also, if the planetesimals are already formed, it is conceivable that the gas disk is already dissipating (especially so close in). I think the authors could be over-estimating the gas density by up to a factor of a 100, which means the stopping time would be a factor of 100 longer.
516: I suggest using another symbol for the temperature power law, since Q is associated with the Toomre value of the disk, for example q. Also, this equation should read T(r) = T_0(r/1AU)^-q, right?
521: Where is that equation coming from? Maybe add reference.

5.2. Gas Drag Force
512: I think it would be very informative to calculate the dimensionless stopping time, i.e. the Stokes number of the planetesimals, I'm assuming that they are substantially above unity, which means that the bodies are essentially decoupled from the gas.
536: Isolation mass lacks definition

5.3 Time-stepping Criterion
554: footnote 2 can just go in the main text body.
584: footnote 3 can also go in the main text body.
584: Are there any works on the numerical robustness of this more efficient time-stepping scheme. While I'm inclined to believe that the error is only marginal, I think having some sort of test (or a reference to one) would make the results more steadfast.
	No there arent. I've added an appendix that compares this timestepping scheme against a fixed timestep case. There appear to be no meaningful differences. TODO: Show mass distribution as differential or cumulative? Finish running sims

### 2023-03-07 main.tex
Add appendix comparing timestepping scheme to fixed steps

>>>>

\appendix
\section{Robustness of Timestepping Scheme}\label{sec:rung_ecc}

As described in section \ref{sec:methods}, {\sc ChaNGa} evolves the motions of the particles in the planetesimal disk using a multi-tiered timestepping scheme. Due to the extremely short dynamical timescale at the inner edge of the disk, the outer disk would require a prohibitive number of timesteps to reach the protoplanet phase using a fixed timestep scheme.To circumvent this, particles are evolved in discrete power-of-two timestep groups. In the event that a collision occurs between two particles on different timesteps, a slight error is introduced to the energy and angular momentum of the merged particle. Due to the nonlinear nature of the runaway growth phase, this slight error tends to trigger more subsequent collisions at the timestep boundary in the disk, and causes protoplanets to preferentially form at the boundaries.

To circumvent this issue, we prohibit particles on different timesteps from merging until the runaway growth phase is well underway. For the fdHi simulation, multi-tiered mergers are not allowed during the first thousand steps. To verify that this technique does not alter the resulting protoplanet distribution in any meaningful way, we ran two test simulations of the inner part (1 to 4 days in orbital period) of the disk from the fdHi simulation. In the first case, the aforementioned timestepping scheme is used. In the second case, all particles are evolved on the timestep appropriate for the inner edge of the disk.

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/rung_ecc.png}
    \caption{A comparison between the innermost region of the fdHi (orange) simulation, and a second version using a fixed timestep appropriate for the inner edge of the disk (green). In the top panel, the period-eccentricity state of the particles is shown, with marker sizes indicating relative mass. The blue points represent the initial state of the simulations. The bottom panel compares the final mass distributions of the bodies (diff or cumulative?).\label{fig:rung_ecc}}
\end{center}
\end{figure}

In figure \ref{fig:rung_ecc}, we compare the final period-eccentricity state and final mass distributions to each other. There do not appear to be any differences between the two protoplanet distributions, particularly near the timestep boundary at 2 days. In addition, the masses of both the protoplanets and the remaining growing planetesimals are indistinguishable. We therefore safely conclude that the timestepping scheme used in this work does not alter the growth of the protoplanets in any meaningful way.
